---
title: "Project 2"
author: "Bryan Alpay"
subtitle: "STATS 220 Semester One 2025"
date: "2025-03-30"
output: 
  html_document:
    code_folding: hide

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, message=FALSE, warning=FALSE, error=FALSE)
```

```{css}
body{
background-color: #001D2D;
color: white;
}
h2{
color: pink;
}
h3{
color: lightyellow;
}

```

## Introduction
### My Data
The focus of my data is on what social media I use, if I should be using the social media right now and how I felt (from 1 to 10, bad to good) about using the social media. Observing and doing the survey every time I use a social media on my mobile phone.


### Guideline to Designing my forms.



### [Google Form Link](https://forms.gle/nwX4ywa2y5rMoLtp9)

## Dynamic Report
[Social Media and Feelings Report Link](https://polkez.github.io/stats220/)


## Creativity
I went beyond by actually using the data and analysing what it will say about myself.

## Learning Reflection


## Appendix
### exploration.R code

```{r file='exploration.R', eval=FALSE, echo=TRUE}

```

### dynamic_report.Rmd code
```{r file='dynamic_report.Rmd', eval=FALSE, echo=TRUE}

```